Fast Regression of the Tritium Breeding Ratio in Tokamak Fusion Reactors

### 2020-05-25 paper/methodology.tex
shorten decoupled methodology section

\subsection{Decoupled Sampling}
\label{sec:experiment-methodology}
\todo{This section needs to be shortened}

The presented surrogate candidates are evaluated in four experimental cases:%
\begin{enumerate}
	\item Hyperparameter tuning in a simplified domain.

	\item Hyperparameter tuning in full domain.

	\item Scaling benchmark.

	\item Model comparison.
\end{enumerate}

The aim of the initial experiments is to use a relatively small subset of
collected TBR samples to determine hyperparameters of considered surrogates.
Since this process requires learning the behaviour of an unknown, possibly
expensive mapping -- here a function that assigns cross-validated metrics to a
point in the hyperparameter domain -- it in many aspects mirrors
the primary task of this work with the notable extension of added utility
to optimise. In order to avoid undesirable exponential slowdown in exhaustive
searches of a possibly high-dimensional parameter space, Bayesian
optimisation~\cite{movckus1975bayesian} is employed as a standard hyperparameter tuning algorithm. We set
its objective to maximise $R^2$ and perform
1000~iterations.\footnote{Hyperparameter tuning of each surrogate family was
	terminated after 2~days. Instances that reached this limit may be identified
	in Table~\ref{tbl:exp1-detailed-results,tbl:exp2-detailed-results} in the
	Appendix.}

In the first experiment, efforts are made to maximise the possibility of success
in surrogates that are prone to suboptimal performance in discontinuous spaces.
This follows the notion that, if desired, performance of such models may be
replicated by training separate instances to model each continuous subregion of
the domain independently.
To this end, data are limited to a single slice from run~2, and discrete
features are completely withheld from evaluated
surrogates. This is repeated for each of the four available slices to
investigate variance in behaviour under different discrete feature assignments.
The second experiment conventionally measures surrogate performance on the full
feature space. Here, in extension of the previous case, surrogates work with
samples comprised of discrete as well as continuous features.

The objective of the last two experiments is to exploit the information gathered by
hyperparameter tuning. In the third experiment, the 20~best-performing
hyperparameter configurations of each family (with respect to~$R^2$) are used to
perform training on progressively larger sets to investigate their scaling
properties. Following that, the fourth experiment aims to produce surrogates
suitable for practical use by retraining selected well-scaling instances on large
training sets to satisfy the goals of this work.

\subsection{Adaptive Sampling}
\label{sec:adaptive}
\todo{This section needs to be shortened}

>>>>

\subsection{Decoupled Approach}\label{sec:experiment-methodology}

Experiments related to the decoupled approach are organised in four parts,
further described in this section. In summary, we aim to optimise hyperparameters of
each surrogate family separately and later use the best found results to compare surrogate
families among themselves.

The objective of the first experiment is to simplify the regression task for
surrogates prone to suboptimal performance in discontinuous spaces.
To this end, training points are filtered to a single selected discrete feature
assignment, and surrogates are trained only on the remaining continuous features.
This is repeated for 4~distinct assignments to explore variances in behaviour.
The second experiment conventionally measures surrogate performance on the full,
unrestricted feature space. In both cases, hyperparameter tuning is
facilitated by Bayesian optimisation~\cite{movckus1975bayesian}. We set its
objective to maximise $R^2$ and terminate the process after 1000~iterations or
2~days, whichever condition is satisfied first.

In the third experiment, the 20~best-performing hyperparameter configurations
per each family are used to train surrogates on sets of various sizes to
investigate their scaling properties. Following that, the fourth experiment aims
to produce surrogates suitable for practical use by retraining selected
well-scaling instances on large training sets in order to satisfy the goals of this work.

\subsection{Adaptive Approach}\label{sec:adaptive}
\todo{This section needs to be shortened}
